Liveness-Based Garbage Collection for Lazy Languages

### 2015-07-06 paper/paper.tex
Added graphs and updated results table

%% \begin{figure}[p]
%% \begin{tabular}{@{}c@{}c@{}}
%% \hskip -4mm{\epsfig{file=sudoku.eps, height=4cm, width=6.10cm}}
%% &
%% {\epsfig{file=lcss.eps, height=4cm, width=6.10cm}}
%% \\
%% \hskip -4mm{\epsfig{file=gc_bench.eps, height=4cm, width=6.10cm}}
%%  &
%% {\epsfig{file=nperm.eps, height=4cm, width=6.10cm}}
%% \\
%% \hskip -4mm{\epsfig{file=fibheap.eps, height=4cm, width=6.10cm}}
%% &
%% {\epsfig{file=knightstour.eps, height=4cm, width=6.10cm}}
%% \\
%% \hskip -4mm{\epsfig{file=nqueens.eps, height=4cm, width=6.10cm}}
%% &
%% {\epsfig{file=treejoin.eps, height=4cm, width=6.10cm}}
%% \end{tabular}
%%  \caption{Memory  usage of  programs. The blue and the red curves
%%   indicate the number of cons cells in the active semi-space for RGC
%% and
%%   LGC respectively. The black curve represents the number of reachable
%%   cells and the grey curve represents the number of cells that are
%%   actually live (of which liveness analysis does  a static
%%   approximation). x-axis is the time measured in number of cons-cells
%%   allocated. y-axis is the number of cons-cells.}
%% \label{fig:memory-usage} \figrule
%% \end{figure}
The table in Figure~\ref{fig:experimental-results} shows that LGC improves the 
garbage collection time and efficiency for most of the programs. 
Even for programs where the time taken is more it is very competitive. 
As the number of garbage collections tend to be very large our graphs show only 
a window which is representative of the behavior for that particular benchmark. 
In all the programs we can see that the curve corresponding to liveness regularly 
dips below the reachability curve.

@@

                            &   \multicolumn{2}{c|}{cells per GC}
                            &   \multicolumn{2}{c|}{cells per GC}
                            &   \multicolumn{2}{c|}{\#GCs}
                            &   \multicolumn{2}{c|}{MinHeap}
                            &   \multicolumn{2}{c|}{Avg. Drag}
                            &   \multicolumn{2}{c|}{(sec)} \\
\cline{2-13}
{Program}    &
RGC & LGC & RGC & LGC  & RGC & LGC  &   RGC & LGC & RGC & LGC & RGC &
LGC \\
\hline
\hline
    {\sf   sudoku}  &381 &1107 &1268 &281 &8 &3 & 1346  &338 &527 &5
&.007 & .034 \\
    {\sf  lcss } & 46522 &51101 &6216 &1363&8&7& 52301  &1701 &5147
&588 &.045 & .144 \\
    {\sf   gc\_bench}  &129179 &131067 &1894 &4&9&9& 131071   &6 &16970
 &4 &.086 & .075 \\
     {\sf  nperm}  & 47586  &174478 &201585 &60882&14&4& 202597  &37507
&171878 &76618 &1.406 & .9  \\
    {\sf  fibheap} &249502  &251525 &5555 &2997&1&1& 254520  &13558
&78720 &0 &.006 & .014  \\
    {\sf  knightstour}  &2593 &314564 &907502 &319299&1161&10&508225
&307092 &206729 &82112 &464.902 & 14.124  \\
    {\sf  treejoin} & 288666  &519943 &297570 &5547&2&1& 525488  &7150
&212653 &1954 &.356 & .217 \\
    {\sf   nqueens} & 283822 &1423226 &2133001 &584143&46&9& 1819579
&501093 &521826 &39465 &70.314 & 24.811 \\
    {\sf   lambda}  &205 & 556 &2072&90345 &23 &8&966 & 721  &303 &95
&.093 &2.49  \\
%    {\sf   fft }& &  & & &&&& ???? &???? &????? &????? &???? & ????
\\
%    {\sf  nboyer} & &  & &   & &  & & &  \\
%    {\sf   circsim?} & &  & &   & & & & &   \\
 \hline
\end{tabular}}

\centerline{(b)}
\vskip -2mm
\caption{Experimental results comparing RGC and LGC. Table (a) gives
  data related to liveness analysis, and (b) gives garbage collection
  data. The average drag time is measured in allocated cons cells.}
\label{fig:experimental-results}
\normalsize
\end{figure*}

>>>>

\begin{figure}[p]
\begin{tabular}{@{}c@{}c@{}}
\hskip -4mm{\epsfig{file=sudoku.eps, height=4cm, width=4.10cm}}
&
{\epsfig{file=lcss.eps, height=4cm, width=4.10cm}}
\\
\hskip -4mm{\epsfig{file=gc_bench.eps, height=4cm, width=4.10cm}}
 &
{\epsfig{file=nperm.eps, height=4cm, width=4.10cm}}
\\
\hskip -4mm{\epsfig{file=fibheap.eps, height=4cm, width=4.10cm}}
&
{\epsfig{file=fibheap.eps, height=4cm, width=4.10cm}}%%Add knightstour.eps
\\
\hskip -4mm{\epsfig{file=nqueens.eps, height=4cm, width=4.10cm}}
&
{\epsfig{file=treejoin.eps, height=4cm, width=4.10cm}}
\end{tabular}
 \caption{Memory  usage  of programs.  The  blue  and the  red  curves
   indicate the number of cons cells  in the active semi-space for LGC
   and  RGC respectively.  The black  curve represents  the number  of
   reachable cells and  the grey curve represents the  number of cells
   that are  actually live (of  which liveness analysis does  a static
   approximation). x-axis is the time measured in number of cons-cells
   allocated. y-axis is the number of cons-cells.}
\label{fig:memory-usage} \figrule
\end{figure}
The  table  in  Figure~\ref{fig:experimental-results} shows  that  LGC
improves the  garbage collection time  and efficiency for most  of the
programs.  Even for  programs where the time taken is  more it is very
competitive.  Memory usage  graphs are shown for  select benchmarks in
Figure~\ref{fig:memory-usage}.  As  the number of  garbage collections
tend  to  be  very large  our  graphs  show  only  a window  which  is
representative of the behavior for  that particular benchmark.  In all
the programs we can see that  the curve corresponding to LGC regularly
dips below the RGC curve.

@@

                            &   \multicolumn{2}{c|}{cells per GC}
                            &   \multicolumn{2}{c|}{cells per GC}
                            &   \multicolumn{2}{c|}{\#GCs}
                            &   \multicolumn{2}{c|}{MinHeap}
                            &   \multicolumn{2}{c|}{Avg. Drag}
                            &   \multicolumn{2}{c|}{(sec)} \\
\cline{2-13}
{Program}    &
RGC & LGC & RGC & LGC  & RGC & LGC  &   RGC & LGC & RGC & LGC & RGC &
LGC \\
\hline
\hline
    {\sf   sudoku}  &381 &1107 &1268 &281 &169 &159 & 1346  &338 &527 &5
&.008 & .026 \\
    {\sf  lcss } & 46522 &51101 &6216 &1363&30&24& 52301  &1701 &5147
&588 &.007 & .008 \\
    {\sf   gc\_bench}  &129179 &131067 &1894 &4&34&4& 131071   &6 &16970
 &4 &.13 & .0002 \\
     {\sf  nperm}  & 47586  &174478 &201585 &60882&710&386& 202597  &37507
&171878 &76618 &0.250 & .154  \\
    {\sf  fibheap} &249502  &251525 &5555 &2997&1002&975& 254520  &13558
&78720 &0 &1.185 & 5.457  \\
    {\sf  knightstour}  &2593 &314564 &907502 &319299&1161&10&508225
&307092 &206729 &82112 &464.902 & 14.124  \\
    {\sf  treejoin} & 288666  &519943 &297570 &5547&116&81& 525488  &7150
&212653 &1954 &4.335 & 4.4 \\
    {\sf   nqueens} & 283822 &1423226 &2133001 &584143&46&9& 1819579
&501093 &521826 &39465 &70.314 & 24.811 \\
    {\sf   lambda}  &205 & 556 &2072&90345 &775 &750&966 & 721  &303 &95
&.179 &1.01  \\
%    {\sf   fft }& &  & & &&&& ???? &???? &????? &????? &???? & ????
\\
%    {\sf  nboyer} & &  & &   & &  & & &  \\
%    {\sf   circsim?} & &  & &   & & & & &   \\
 \hline
\end{tabular}}

\centerline{(b)}
\vskip -0.75mm
\caption{Experimental results comparing RGC and LGC. Table (a) gives
  data related to liveness analysis, and (b) gives garbage collection
  data. The average drag time is measured in allocated cons cells.}
\label{fig:experimental-results}
\normalsize
\end{figure*}
